---
title: "Covid-19 CZ: selected data for the Czech Republic"
---

```{r setup, include=F}

knitr::opts_chunk$set(fig.retina = 3, echo = F, eval = T,
                      warning = F,
                      out.width = "90%",
                      dev = "ragg_png",
                      fig.showtext = T,
                      message = F)

knitr::opts_knit$set()

library(stringr)
library(dplyr)
library(ggplot2)
library(czso)
library(CzechData)
library(lubridate)
library(ragg)
library(ptrr)
library(scales)
library(fontawesome)
library(tidyverse)
library(pragr)
library(ggiraph)
library(rmapshaper)

Sys.setlocale("LC_TIME", "cs_CZ.UTF-8")

ptrr::set_geom_defaults()
update_geom_defaults("rect", list(fill = "blue"))
```

```{r fonts}
sysfonts::font_add_google("IBM Plex Sans", "Roboto")
sysfonts::font_add_google("IBM Plex Sans Condensed", "Roboto Condensed")
```

```{r metathis}
library(metathis)

meta() %>%
  meta_description(
    "Vybraná data o Covid-19 v ČR"
  ) %>% 
  meta_name("github-repo" = "petrbouchal/covid") %>% 
  meta_viewport() %>% 
  meta_social(
    title = "Czech Track",
    url = "https://petrbouchal.github.io/covid/",
    image = "https://petrbouchal.github.io/covid/twitter_card_large.png",
    image_alt = "Náhled grafu nárůstu případů podle okresů",
    og_type = "website",
    og_author = c("Petr Bouchal"),
    twitter_card_type = "summary_large_image",
    twitter_creator = "@petrbouchal"
  )
```

# {.tabset}

## Cases by district {.tabset .tabset-pills} 

```{r case-data-load}
cisokr <- czso_get_codelist(109) %>% 
  select(okres_lau_kod = CHODNOTA, okres = ZKRTEXT)
ciskraj <- czso_get_codelist(108) %>% 
  select(kraj_nuts_kod = CHODNOTA, kraj = ZKRTEXT)

nhs <- read_csv("https://onemocneni-aktualne.mzcr.cz/api/v2/covid-19/nakaza.csv")

nhs_bd <- read_csv("https://onemocneni-aktualne.mzcr.cz/api/v2/covid-19/osoby.csv") %>% 
  left_join(cisokr) %>% 
  left_join(ciskraj)

nhs_okr <- read_csv("https://onemocneni-aktualne.mzcr.cz/api/v2/covid-19/kraj-okres-nakazeni-vyleceni-umrti.csv") %>% 
  left_join(cisokr) %>% 
  left_join(ciskraj)

umrti <- read_csv("https://onemocneni-aktualne.mzcr.cz/api/v2/covid-19/umrti.csv") %>% 
  left_join(cisokr) %>% 
  left_join(ciskraj)

epis <- read_csv("https://onemocneni-aktualne.mzcr.cz/api/v2/covid-19/kraj-okres-nakazeni-vyleceni-umrti.csv")
```


```{r okresy-geo-load}
okresy_p <- read_rds("okresy_polygons.rds")
```

```{r populace}
obyv_praha <- czso_get_table("130141r20") %>% 
  filter(idhod == "830959865") %>% 
  select(hodnota) %>% 
  mutate(okres_lau_kod = "CZ0100")

obyv_okresy <- czso_get_table("130141r20") %>% 
  filter(vuzemi_cis == "101", vuk_text == "Střední stav obyvatel") %>% 
  left_join(czso_get_codelist(101) %>% 
              select(okres_lau_kod = CZNUTS, vuzemi_kod = CHODNOTA)) %>% 
  rows_insert(obyv_praha) %>% 
  rename(pocobyv = hodnota)
```


```{r model, eval=F}
lm_okres <- function(df) {
  lm(kumulativni_pocet_nakazenych ~ as.numeric(datum), data = df)
}

epis %>% 
  group_by(okres_lau_kod) %>% 
  # mutate(kumulativni_pocet_nakazenych = na_if(kumulativni_pocet_nakazenych, 0)) %>% 
  nest() %>% 
  mutate(model = map(data, lm_okres)) %>% 
  mutate(glance = map(model, broom::glance)) %>% 
  unnest(glance) %>%
  # select(-data, -model) %>% 
  ungroup() %>% 
  skimr::skim()
```

```{r weeks, eval = T}
last_week <- today() - period(1, "week")
last_week_fmt <- ptrr::format_date_human(last_week)
```

```{r narust}
nhs_narust <- nhs_bd %>%
  filter(datum >= last_week) %>%
  group_by(okres, okres_lau_kod, datum) %>% 
  summarise(pocet = n(), .groups = "drop") %>% 
  complete(okres, datum, fill = list(pocet = 0)) %>% 
  drop_na(okres) %>%
  left_join(obyv_okresy %>% select(okres_lau_kod, pocobyv)) %>% 
  group_by(okres) %>% 
  filter(sum(pocet) > 5) %>% 
  arrange(okres, datum) %>%
  mutate(narust = cumsum(pocet), narust_perk = narust/pocobyv * 100000) %>% 
  ungroup() %>% 
  mutate(okres = fct_reorder(okres, narust, max, na.rm = T, .desc = T))
```

```{r days-since-data}
lastpos <- nhs_bd %>% 
  group_by(okres, okres_lau_kod) %>% 
  summarise(last_pos = max(datum)) %>% 
  mutate(days_since_last = today() - last_pos) %>% 
  arrange(desc(days_since_last))

lastwk <- nhs_bd %>% 
  left_join(obyv_okresy %>% select(okres_lau_kod, pocobyv)) %>% 
  drop_na(okres) %>% 
  filter(datum > last_week) %>% 
  group_by(okres, okres_lau_kod) %>% 
  summarise(pocet = n(), pocobyv = mean(pocobyv), pocet_perk = pocet/pocobyv*100000)
```

### Cases last 7 days

```{r map-cases}
library(patchwork)

okresy_percap_plot <- okresy_p %>% 
  left_join(lastwk, by = c("lau1_kod" = "okres_lau_kod")) %>% 
  drop_na(okres) %>%
  mutate(tooltip = paste0(okres, "\n", label_number_cz(1)(pocet_perk))) %>% 
  # replace_na(list(pocet = 0)) %>% 
  ggplot(aes(fill = pocet_perk, data_id = lau1_kod, tooltip = tooltip)) +
  geom_sf_interactive(colour = NA) +
  scale_fill_binned(na.value = "grey", n.breaks = 6,
                    labels = label_number_cz(accuracy = 1),
                    type = "viridis",
                    limits = c(min(lastwk$pocet_perk), max(lastwk$pocet_perk))) +
  guides(fill = guide_bins(title = NULL, direction = "vertical", override.aes = list(colour = NA),
                           show.limits = T, ticks = F, even.steps = T, axis = T, reverse = F)) +
  theme_void() +
  theme(legend.position = "right", legend.justification = 0) +
  labs(title = "Počet nových případů za posledních 7 dní",
       subtitle = "Na 100 tisíc obyvatel")

okresy_abs_plot <- okresy_p %>% 
  left_join(lastwk, by = c("lau1_kod" = "okres_lau_kod")) %>% 
  drop_na(okres) %>%
  mutate(tooltip = paste0(okres, "\n", label_number_cz(1)(pocet))) %>% 
  # replace_na(list(pocet = 0)) %>% 
  ggplot(aes(fill = pocet, data_id = lau1_kod, tooltip = tooltip)) +
  geom_sf_interactive(colour = NA) +
  scale_fill_binned(na.value = "grey", n.breaks = 7,
                    labels = label_number_cz(accuracy = 1),
                    limits = c(min(lastwk$pocet), max(lastwk$pocet)),
                    type = "viridis"
                    ) +
  guides(fill = guide_bins(title = NULL, direction = "vertical", 
                           override.aes = list(colour = NA),
                           show.limits = T, ticks = F, even.steps = T, axis = T, reverse = F)) +
  theme_void() +
  theme(legend.position = "right", legend.justification = 0,
        text = element_text(family = "IBM Plex Sans")) +
  labs(subtitle = "Absolutně")

girafe(code = print(okresy_percap_plot / okresy_abs_plot), 
       fonts = list(sans = "IBM Plex Sans"), 
       options = list(opts_sizing(width = 1),
                      opts_tooltip(css = "font-family: IBM Plex Sans; color:white; background-color: black; padding:6px;border-radius:5px;"),
                      opts_hover(css = "stroke: white")))
```

### Growth by district since `r last_week_fmt`



```{r narust-plot}
nhs_narust %>% 
  filter(max(pocet, na.rm = T) > 0) %>%
  ggplot(aes(datum, narust)) +
  geom_line(colour = "darkblue", size = 1) +
  geom_point(colour = "darkblue", size = 1.5) +
  facet_wrap(facets = vars(okres), scales = "free_y") +
  scale_y_continuous(expand = expansion(add = c(60, 60))) +
  scale_x_date(labels = label_date_short(format = c(NA, "%b", "%d", "%h")), 
               breaks = breaks_width("2 days")) +
  ptrr::theme_ptrr("y", multiplot = T) +
  theme(axis.text.x = element_text(hjust = 0))
```


```{r narust-tab, eval=F}
nhs_bd %>% 
  filter(datum > "2020-07-13") %>%
  mutate(okr_grp = fct_lump_n(okres, 10, other_level = "Ostatní")) %>%
  drop_na(okr_grp) %>% 
  count(okr_grp, sort = F) %>% 
  ungroup() %>% 
  mutate(okr_grp = fct_reorder(okr_grp, n, .desc = T) %>% 
           fct_relevel("Ostatní", after = Inf)) %>% 
  arrange(okr_grp)
```


```{r map-days-since, eval=F}
### Days since last case in each district
lastpos_ch <- okresy_p %>% 
  left_join(lastpos, by = c("lau1_kod" = "okres_lau_kod")) %>% 
  drop_na(okres)

lastpos_g <- ggplot(lastpos_ch, aes(fill = as.integer(days_since_last))) +
  geom_sf_interactive(aes(data_id = okres, tooltip = paste0(okres, "\n", days_since_last))) +
  scale_fill_binned(na.value = "grey", show.limits = T, n.breaks = 6,
                    type = "viridis",
                    limits = c(min(lastpos_ch$days_since_last),
                               max(lastpos_ch$days_since_last)) %>%
                      as.integer()) +
  guides(fill = guide_coloursteps(even.steps = F,
                                  title = NULL, direction = "horizontal",
                                  show.limits = T, ticks = F)) +
  theme_void() +
  theme(legend.position = c(.8, .8))

girafe(ggobj = lastpos_g, fonts = list(sans = "IBM Plex Sans"), 
       options = list(opts_sizing(width = 1),
                      opts_tooltip(css = "font-family: IBM Plex Sans; color:white; background-color: black; padding:6px;border-radius:5px;"),
                      opts_hover(css = "stroke: white")))
```

## Cases by age {.tabset .tabset-pills} 

```{r age-grid}
cases_base <- nhs_bd %>% 
  filter(datum > "2020-08-01", vek < 130) %>% 
  mutate(vek = cut_width(vek, width = 15, boundary = 0, ordered_result = T) %>% 
           fct_relabel(str_remove_all, "\\(|\\)|\\]|\\[") %>% 
           fct_relabel(str_replace, "\\,", " - "),
         pocet = 1)

cases_grid <- cases_base %>% 
  select(datum, kraj, vek) %>% 
  expand(kraj, datum = full_seq(datum, 1), vek)
```

```{r}
make_plot_base <- function(data) {ggplot(data) + 
  guides(fill = guide_colorbar(title.position = "left", barwidth = unit(5, "cm"), 
                               draw.ulim = T, 
                               title.vjust = .75)) +
  ptrr::theme_ptrr(multiplot = F, 
                   axis.text = element_text(colour = "black"),
                   axis.text.x = element_text(hjust = 0),
                   axis.title.x = element_text(hjust = 0, 
                                               margin = margin(c(0.4,0,0,0), "cm")),
                   legend.position = "bottom",
                   legend.margin = unit(c(0,0,0,0), "cm"),
                   legend.box.margin = unit(c(0,0,0,0), "cm"),
                   legend.direction = "horizontal") +
  scale_x_date(date_breaks = "week", labels = label_date_short(),
               expand = expansion(0, 0))}
```


```{r age-heatmap-base}
heatmap_basedt <- cases_grid %>% 
  left_join(cases_base) %>% 
  mutate(week = isoweek(datum),
         datum_orig = datum) %>% 
  mutate(datum =  as.Date(paste(2020, week, 1, sep="-"), "%Y-%U-%u") - days(6))

heatmap_basedt_kraje <- heatmap_basedt %>% 
  group_by(kraj, datum, vek) %>%
  filter(datum > "2020-08-01") %>% 
  summarise(pocet = sum(pocet, na.rm = T)/n_distinct(datum_orig), .groups = "drop") %>% 
  complete(kraj, datum, vek) %>%
  replace_na(replace = list(pocet = 0)) %>% 
  group_by(kraj, datum) %>%
  mutate(all_ages = sum(pocet, na.rm = T)) %>% 
  group_by(kraj, datum) %>%
  mutate(podil = pocet/all_ages) %>% 
  drop_na(kraj)

heatmap_basedt_cr <- heatmap_basedt %>% 
  group_by(datum, vek) %>% 
  filter(datum > "2020-08-01") %>% 
  summarise(pocet = sum(pocet, na.rm = T)/n_distinct(datum_orig), .groups = "drop") %>% 
  complete(datum, vek) %>% 
  replace_na(replace = list(pocet = 0)) %>% 
  group_by(datum) %>% 
  mutate(all_ages = sum(pocet, na.rm = T)) %>% 
  group_by(datum) %>% 
  mutate(podil = pocet/all_ages)
```

### National

```{r age-heatmap-cr-count}
make_plot_base(heatmap_basedt_cr) +
  scale_fill_viridis_c(option = "B", labels = label_number_cz(),
                       n.breaks = 6,
                       name = "Průměrný denní počet nových případů") + 
  geom_tile(aes(datum, vek, fill = pocet)) +
  labs(title = "Nové případy podle věku, po týdnech", x = "Týden začínající...",
       subtitle = "Průměrný denní počet nových případů v daném týdnu")
```

### National (%)

```{r age-heatmap-cr-share}
make_plot_base(heatmap_basedt_cr) +
  scale_fill_viridis_c(option = "B", labels = label_percent_cz(1),
                       name = "Podíl věkové skupiny v daném týdnu") + 
  geom_tile(aes(datum, vek, fill = podil)) +
  guides(fill = guide_colorbar(title.position = "left", barwidth = unit(5, "cm"), 
                               title.vjust = .75)) +
  labs(title = "Věkové složení nových případů po týdnech", subtitle = "",
       x = "Týden začínající...", y = NULL)
```

### By region

```{r age-heatmap-kraje-count}
make_plot_base(heatmap_basedt_kraje) +
  scale_fill_viridis_c(option = "B", labels = label_number_cz(),
                       n.breaks = 6,
                       name = "Denní počet nových případů") + 
  facet_wrap(~ kraj) +
  geom_tile(aes(datum, vek, fill = pocet)) +
  guides(fill = guide_colorbar(title.position = "top", barwidth = unit(5, "cm"))) +
  theme(legend.position = c(.75, .02),
        axis.text = element_text(size = 8)) +
  labs(title = "Nové případy podle věku, po týdnech",
       x = "Týden začínající...")
```

### By region (%)

```{r age-heatmap-kraje-share}
make_plot_base(heatmap_basedt_kraje) +
  scale_fill_viridis_c(option = "B", labels = label_percent_cz(1),
                       name = "Podíl věkové skupiny v daném týdnu") + 
  facet_wrap(~ kraj) +
  geom_tile(aes(datum, vek, fill = podil)) +
  guides(fill = guide_colorbar(title.position = "top", barwidth = unit(5, "cm"))) +
  theme(legend.position = c(.75, .02), , 
        legend.margin = unit(c(0,0,0,0), "cm"),
        legend.direction = "horizontal",
        axis.text = element_text(size = 8)) +
  labs(title = "Věkové složení nových případů po týdnech",
       x = "Týden začínající...")
```

## Deaths by age

```{r}
umrti_base <- umrti %>% 
  mutate(vek = cut_width(vek, width = 10, boundary = 0, ordered_result = T) %>% 
           fct_relabel(str_remove_all, "\\(|\\)|\\]|\\[") %>% 
           fct_relabel(str_replace, "\\,", " - "),
         pocet = 1)

umrti_grid <- umrti_base %>% 
  select(vek, datum) %>% 
  expand(vek, datum = full_seq(datum, 1))

umrti_heatmap_dt <- umrti_grid %>% 
  left_join(umrti_base) %>% 
  mutate(week = isoweek(datum),
         week_starting = as.Date(paste(2020, week, 1, sep="-"), "%Y-%U-%u") - days(6)) %>% 
  group_by(week_starting, vek) %>%
  summarise(pocet = sum(pocet, na.rm = T)/n_distinct(datum), .groups = "drop") %>% 
  replace_na(replace = list(pocet = 0)) %>% 
  group_by(week_starting) %>%
  mutate(weekly_total = sum(pocet, na.rm = T)) %>% 
  group_by(week_starting) %>%
  mutate(podil = pocet/weekly_total)
```


```{r}
make_plot_base(umrti_heatmap_dt) +
  scale_fill_viridis_c(option = "B", labels = label_number_cz(1),
                       name = "Počet úmrtí v daném týdnu") + 
  geom_tile(aes(week_starting, vek, fill = pocet)) +
  labs(title = "Úmrtí podle věku",
       subtitle = "Průměrný denní počet úmrtní v daném týdnu",
       x = "Týden začínající...")
```


## Mortality statistics {.tabset .tabset-pills}

```{r mort-data}
zmr0 <- czso_get_table("130185", force_redownload = T)
zmr <- zmr0 %>% 
  mutate(tyden = as.numeric(tyden),
         casref_do = as.Date(casref_do),
         day_sameyear = make_date(1970, month = month(casref_do),
                                  day = day(casref_do))) %>% 
  mutate(vek_txt = fct_relevel(vek_txt, "celkem"))

last_date_fmt <- ptrr::format_date_human(max(zmr$casref_do))
today_fmt <- ptrr::format_date_human()
```

```{r time-adjusting}
# vek <- czso::czso_get_table("130142")
# write_csv(vek, "vek.csv")
vek <- read_csv("vek.csv")

# vek_ciselnik <- czso::czso_get_codelist("cis7700")
# write_csv(vek_ciselnik, "vek_ciselnik.csv")
vek_ciselnik <- read_csv("vek_ciselnik.csv")

vek_prevodnik <- read_csv("vek-prevodnik.csv")

vek_slct <- vek %>%  
  filter(vuzemi_cis == "97") %>% 
  filter(is.na(pohlavi_txt)) %>% 
  left_join(vek_ciselnik %>%
                    select(vek_kod = CHODNOTA, zkr = ZKRTEXT, 
                           txt = TEXT, matches("MIN|MAX"))) %>% 
  select(idhod, hodnota, vek_txt, zkr, txt, casref_do) %>% 
  left_join(vek_prevodnik) %>% 
  group_by(casref_do, vek_txt = vek_grp) %>% 
  summarise(pocet_obyv = sum(hodnota, na.rm = T)) %>% 
  mutate(rok = year(casref_do)) %>% 
  ungroup() %>% 
  select(-casref_do)

vek_slct_withsum <- vek_slct %>% 
  bind_rows(vek_slct %>% 
              group_by(rok) %>% 
              summarise(pocet_obyv = sum(pocet_obyv)) %>% 
              mutate(vek_txt = "celkem"))

vek_do2020 <- vek_slct_withsum %>% 
  bind_rows(vek_slct_withsum %>% 
              filter(rok == 2019) %>% 
              mutate(rok = 2020))

zmr_normd <- zmr %>% 
  left_join(vek_do2020) %>% 
  mutate(normd = hodnota/pocet_obyv * 1e5)

zmr_bands <- zmr_normd %>% 
  mutate(is2020 = rok == 2020) %>% 
  mutate(day_sameyear_floored = floor_date(day_sameyear, "weeks")) %>% 
  group_by(is2020, vek_txt, tyden, day_sameyear_floored) %>% 
  summarise(min = min(normd, na.rm = T), 
            max = max(normd, na.rm = T), .groups = "drop") %>% 
  mutate(vek_txt = fct_relevel(vek_txt, "celkem"))
```

### Standardised

```{r}
lbs_grey <- tribble(~vek_txt, ~day_sameyear_floored, ~min, ~txt,
               factor("celkem"), as.Date("1970-05-01"), 12.1, "rozpětí\n2011-19",
               )
lbs_blue <- tribble(~vek_txt, ~day_sameyear_floored, ~min, ~txt,
               factor("celkem"), as.Date("1970-02-15"), 11.5, "2020"
               )
```


```{r age-adjusted-plot}
ggplot(data = zmr_bands, mapping = aes(group = vek_txt)) +
  geom_ribbon(data = zmr_bands %>% filter(!is2020),
              alpha = 0.3,
              aes(x = day_sameyear_floored, ymin = min, ymax = max)) +
  geom_line(data = zmr_bands %>% filter(is2020),
            colour = "darkblue",
            aes(x = day_sameyear_floored, y = min)) +
  geom_point(data = zmr_bands %>% filter(is2020),
            aes(x = day_sameyear_floored, y = min), size = .5, colour = "white") +
  facet_wrap(~vek_txt, scales = "free_y") +
  scale_x_date(date_breaks = "3 months",
               date_labels = "%b", breaks = c(1,3,6, 9, 12)) +
  theme_ptrr("y", multiplot = T) +
  labs(x = "Týden v roce",
       subtitle = str_glue("Poslední data k {last_date_fmt}. Modrá = 2020, šedá = rozpětí let 2011-2019"),
       title = "Zemřelí na 100 000 obyv. podle týdnů v roce, 2011-2020",
       caption = str_glue("Výpočet dle dat ČSÚ, sada 130185 (úmrtí) a 130142 (věk) | @petrbouchal {today_fmt}")) +
  geom_text(data = lbs_grey, aes(x = day_sameyear_floored, 
                            y = min, label = txt), 
            fontface = "bold",
            colour = "grey40",size = 2) +
  geom_text(data = lbs_blue, aes(x = day_sameyear_floored, 
                            y = min, label = txt), 
            fontface = "bold",
            colour = "darkblue", size = 2)
```


```{r mort-base}
zemr_plot_base <- zmr %>% 
  ggplot(aes(day_sameyear, hodnota,
             alpha = rok == 2020, size = rok == 2020)) +
  geom_line(aes(colour = as.factor(rok), group = rok)) +
  scale_alpha_manual(values = c(`TRUE` = 1, `FALSE` = .4), guide = "none") +
  scale_size_manual(values = c(`TRUE` = .7, `FALSE` = .4), guide = "none") +
  scale_colour_viridis_d(direction = -1, name = "rok") +
  ptrr::theme_ptrr("both", multiplot = T, axis.title.x = element_text()) +
  labs(x = "Týden v roce",
       subtitle = str_glue("Poslední data k {last_date_fmt}, staženo {today_fmt}"),
       title = "Počty zemřelých podle týdnů v roce, 2011-2020",
       caption = "Data: ČSÚ, sada 130185 | @petrbouchal") +
  scale_x_date(date_breaks = "3 months", date_labels = "%b", breaks = c(1,3,6, 9, 12)) +
  theme(axis.text.x = element_text(hjust = 0))
```

### Raw counts (comparison)

```{r mort-plot-fixed}
zemr_plot_base +
  facet_wrap(~vek_txt)
```

### Raw counts (detail)

```{r mort-plot-free}
zemr_plot_base +
  facet_wrap(~vek_txt, scales = "free_y")
```

## Data & disclaimer

This repository contains code that generates a dashboard using open data on Covid-19 cases and deaths in the Czech Republic, and on all-cause mortality to understand excess deaths.

The goal is to provide some of the comparisons that official sources (e.g. the Czech Health Ministry at https://onemocneni-aktualne.mzcr.cz/covid-19) do not provide - namely a per-district view of recent cases and the age breakdown of cases and deaths over time.

The Covid-19 data comes from UZIS, the Czech health data authority, via data published by the Czech Ministstry of Health at https://onemocneni-aktualne.mzcr.cz/covid-19.

The mortality data comes from the Czech Statistical Office: https://www.czso.cz/csu/czso/obypz_cr. It is reported with a delay of several weeks owing to the manual process of recording and reporting deaths in population registers.

### Important

The data visualisations should be taken with a grain of salt. The data is incomplete and imperfect: it can undergo backward revisions, fresh data sometimes contains errors, and there are issues inherent in how the data is collected and reported (starting from test errors, to reporting errors, to time inconsistencies etc.)

Specifically, daily figures, where reported, are subject to change and significant variation and these should be intepreted with caution. 

# 

Last built on `r format(lubridate::now("CET"), "%Y-%m-%d %H:%M %Z")`
